\chapter{MyMPILib}
Basic interface to an mpi implementation, so the code requires no
mpi specific commands.
Utilizes a scheduler-worker model:
\begin{itemize}
  \item scheduler - manager, distributes work and collects results
  \item worker - does actual calculations
\end{itemize}

\section{How to use}
Need to write scheduler module and wuGenericWorkunit module for your
code.
Former usally only needs to overwrite the specific part.

\section{Code}
Code distributed into three folders - Generic, Internal and Specific.
Makes use of includes.

these will include other files:
scheduler\_header.f90
scheduler\_generic.f90
scheduler\_module.f90

where the scheduler\_module will include the other two, and scheduler\_specific
Modules included are listener, comListener, wuListener, dispatcher,
comDispatcher and wuDispatcher.

wu - work unit?

\section{Todo}
\begin{itemize}
  \item Add checkpointing? Could be based on unit of work, maybe needs
  to be implemented in specific code instead.
\end{itemize}


Types:
type :: scheduler

type, abstract :: packable
  type, extends(packable) :: matrix
  type, extends(packable), abstract :: workunit
    type, extends(workunit) :: genericWorkunit
      type, extends(genericWorkunit) :: wuMergeWorkunit
        type, extends(wuMergeWorkunit) :: wuMergeChunk
      type, extends(genericWorkunit) :: wuDataRequester
      type, extends(genericworkunit) :: initWorkunit

type :: dispatcher !< Sending signals?
  type, extends(dispatcher) :: wuDispatcher
  type, extends(dispatcher) :: comDispatcher

type :: listener !< Receiving signals?
  type, extends(listener) :: wuListener
  type, extends(listener) :: comListener

type :: globalSchedulerStorage
type :: packBuffer
type :: commandline_parser
type :: configFileParser
type :: mpelog
type :: myLogClass
type :: clientStatus

type :: node
  type, extends(node) :: packableNode
  type, extends(node) :: workunitNode
  type, extends(node) :: intnode

type :: list
  type, extends(list) :: packableList
  type, extends(list) :: workunitList
  type, extends(list) :: intlist
